\documentclass[a4paper,10pt]{article}
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fontawesome5} % Add this in the preamble
\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{SHARATH VN}} \\
    \vspace{0.2cm}
    \small
    \faEnvelope\ \href{mailto:sharathnarayan16@gmail.com}{sharathnarayan16@gmail.com} \ | \
    \faPhone\ +91-7619398922 \ | \
    \faLinkedin\ \href{https://www.linkedin.com/in/sharath-vn-93160920b/}{LinkedIn} \ | \
    \faGithub\ \href{https://github.com/sharath56}{GitHub} \ | \
    \faFlag\ India \ | \ \faMapMarker*\ Chikkaballapur
\end{center}


\vspace{0.2cm}
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}



\vspace{0.5cm}

\section*{Professional Summary}
Senior Engineer with over 3 years of practical experience in developing data acquisition systems, video data analysis pipelines, and IMU data processing solutions. Proficient in multi-sensor integration, including the synchronization of various camera types for real-time applications. Experienced in building ROS2-based systems for deployment in production environments. Background includes the design and deployment of AI-powered tools and embedded AI solutions, with a track record of delivering end-to-end systems from initial research through to final production.

\vspace{0.3cm}

\section*{Technical Skills}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Programming \& AI:} Python, FastAPI, PyTorch, TensorFlow, OpenCV, YOLO (v5, v11-OBB, YOLO-Seg)
    \item \textbf{Embedded Systems:} ESP32, Raspberry Pi, NVIDIA Jetson, real-time data acquisition and monitoring
    \item \textbf{Sensor \& Video Integration:} IMU, wide-angle, fisheye, 360° cameras (GoPro, GoPro Max)
    \item \textbf{AI Deployment:} Azure ML, Google Coral, ONNX Runtime, Edge AI solutions
    \item \textbf{Robotics \& Perception:} ROS2, sensor fusion, multi-camera synchronization
    \item \textbf{Cloud \& DevOps:} Azure, Docker, Git
\end{itemize}

\vspace{0.3cm}

\section*{Professional Experience}

\textbf{Senior Engineer} \hfill \textit{Autoliv India} \\
\textit{Jan 2024 – Present}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Ride-Safe Project (KTM Duke 2023):} Developed a multi-sensor data collection and monitoring system with 360° video capture to analyze Indian road conditions and rider behavior.
    \item \textbf{Ride-Safe Honda (Extended Version):} Expanded the Ride-Safe system for Honda motorcycles, enabling real-time sensor data visualization. Supported instrumentation of 10 motorcycles and resolved field issues in Malaysia.
    \item \textbf{Data Anonymization Pipeline:} Created a privacy-focused video anonymization tool using YOLOv11-OBB, achieving \textbf{94\% accuracy} in face and license plate detection.
    \item \textbf{Honda Video Perception System:} Developing a Python-based pipeline for lane detection, traffic object detection, traffic sign segmentation (YOLO-Seg), fisheye calibration, and monocular depth estimation from fisheye video streams.
\end{itemize}

\vspace{0.2cm}

\textbf{Master Engineer Trainee} \hfill \textit{Autoliv India} \\
\textit{Oct 2022 – Oct 2023}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Ride-Safe Project:} Built ROS2 applications integrating \textbf{Polar H10} (heart and respiration monitoring), \textbf{GoPro Max 360} (front-view capture), and custom bike instrumentation.
    \item \textbf{SITIS Project:} Developed a Python tool for extracting \textbf{GPS}, \textbf{gyroscope}, and \textbf{acceleration data} from BlackVue camera video streams.
    \item \textbf{Vest Airbag Algorithm:} Built an automated crash test pipeline and crash detection model using \textbf{ANN}, trained on wearable IMU and simulated crash data.
\end{itemize}

\vspace{0.2cm}

\textbf{Research Intern} \hfill \textit{Autoliv India} \\
\textit{Apr 2022 – Oct 2022}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Vest Airbag Algorithm:} Developed a \textbf{CNN-based} real-time airbag deployment algorithm with \textbf{95\% accuracy}.
    \item \textbf{Traffic Anonymization System:} Created a real-time traffic monitoring and anonymization tool using \textbf{YOLOv5}.
    \item \textbf{Vest MC Logger Monitoring:} Built automated data monitoring scripts for motorcycle data loggers.
\end{itemize}

\vspace{0.3cm}

\section*{Patents}
\begin{itemize}[leftmargin=1.5em]
    \item Filed an IDF for a PTW (Powered Two-Wheeler) wireless health monitoring system using \textbf{mm-wave radar} for breath and heart rate prediction, including gesture control functionality.
\end{itemize}

\vspace{0.3cm}

\section*{Education}

\textbf{M.Tech in Biomedical Signal Processing and Instrumentation} \hfill \textit{BMS College of Engineering} \\
Graduation Year: 2022

\textbf{B.E in Telecommunication and Electronics Engineering} \hfill \textit{S.J.C Institute of Technology} \\
Graduation Year: 2020

\end{document}
